NTM CT Scoring - Initial Agreement

### 2023-04-04 Stacey Martiniano/ntm_agreement.qmd
Update ntm_agreement.qmd
polychoric ready to go

```{r}
# Remove scans and features with no variability
df_list = split.data.frame(data,f = ~ scan_id + feature)
perfect_agreement = lapply(df_list,function(d){
  if(all(d$disagree==FALSE) | all(d$disagree==TRUE)){
    return(names(d))
  } else {
    return(NA)
  }
})
boot_df = data
```

@@

```{r}

```

>>>>

```{r}
# Remove scans and features with no variability
df_list = split.data.frame(data,f = ~ scan_id + feature)
perfect_agreement = lapply(df_list,function(d){
  if(all(d$disagree==FALSE) | all(d$disagree==TRUE)){
    return(names(d))
  } else {
    return(NA)
  }
})
```

@@

```{r}
library(psych)
boot_polychor <- function(df, i) {
  d <- df[i,c("AF","DL","JW")] # allows boot to select sample
  d = data.matrix(d)
  p = suppressWarnings(polychoric(d,global = F,correct = F))
  p = p$rho[lower.tri(p$rho)]
  names(p)=c("AF-DL","AF-JW","DL-JW")
  return(p)
}
```

```{r}
pa <- boot(data,boot_polychor,R=1000,strata = interaction(factor(data$scan_id),factor(data$location)))
ci_af_dl=boot.ci(pa,index = 1,type = c("perc","bca"))
ci_af_jw=boot.ci(pa,index = 2,type = c("perc","bca"))
ci_dl_jw=boot.ci(pa,index = 3,type = c("perc","bca"))
```
